---
title: "RF measurements analysis"
output: html_document
date: "2023-10-27"
---
# Entwicklungsumgebung
**Libraries**
```{r}
#install.packages("bit64")
```

```{r}
library(arsenal)
library(ggplot2)
library(bit64)
```
**Environment**
```{r}
rm(list=ls())
setwd(getwd())

constant <- list()
```
**Verweise**
```{r}
paths <- list (
  raw_dataset = "./raw"
)
files_dataset <- list (
  "example"
)
```
# Dataset Measurments
## Raw
```{r}
dataset_path = file.path(paths$raw_data, files_dataset[1])
dataset_files <- list (
  send = file.path(dataset_path, "test_data_send.txt"),
  receive = file.path(dataset_path, "test_data_received.txt")
)
dataset_raw <- list (
  send = read.csv(dataset_files$send, header = FALSE, sep = ",", dec = "."),
  receive = read.csv(dataset_files$receive, header = FALSE, sep = ",", dec = ".")
)

colnames(dataset_raw$send) <- c("id", "time", "sensor_1")
colnames(dataset_raw$receive) <- c("id", "time", "sensor_1", "rssi")

# Check
is.data.frame(dataset_raw$send)
is.data.frame(dataset_raw$receive)
```

*Fix semicolons*
```{r}
dataset_raw$send$sensor_1 <- gsub(";", "", dataset_raw$send$sensor_1)
dataset_raw$receive$sensor_1 <- gsub(";", "", dataset_raw$receive$sensor_1)
```

*Dataset raw values*
```{r}
print(dataset_raw$send)
print(dataset_raw$receive)
```
## Processed
```{r}
dataset_processed <- list (
  send = dataset_raw$send,
  receive = dataset_raw$receive
)
# convert sensor values
dataset_processed$send$sensor_1d <- strtoi(dataset_raw$send$sensor_1, base = 2)
dataset_processed$receive$sensor_1d <- strtoi(dataset_raw$receive$sensor_1, base = 2)

colnames(dataset_processed$send) <- c("id", "time", "sensor_1b", "sensor_1d")
colnames(dataset_processed$receive) <- c("id", "time", "sensor_1b", "rssi", "sensor_1d")

# Check
is.data.frame(dataset_processed$send)
is.data.frame(dataset_processed$receive)
```

*Dataset processed values*
```{r}
print(dataset_processed$send)
print(dataset_processed$receive)
```
### Unify
```{r}
dataset_processed$send_unified <- dataset_processed$send
dataset_processed$receive_unified <- dataset_processed$receive
# names
dataset_processed$send_unified$set_name <- "send"
dataset_processed$receive_unified$set_name <- "receive"
# unify columns 
dataset_processed$receive_unified$rssi <- NULL
```
### merge data frames
```{r}
# merge
dataset_processed$send_rec <- rbind(
  dataset_processed$receive_unified, 
  dataset_processed$send_unified
)
print(dataset_processed$send_rec)
#print(dataset_processed$receive_unified)
#print(dataset_processed$send_unified)
```

# Compare
```{r}
compare <- list()
```

## send - received
```{r}
compare$send_rec <- comparedf(dataset_processed$send_unified, dataset_processed$receive_unified)
compare$send_rec_summary <- summary(compare$send_rec)
```
```{r}
compare$send_rec_summary$frame.summary
```
```{r}
print("number of packages difference")
compare$packages_diff = length(dataset_processed$send_unified$id) -
  length(dataset_processed$receive_unified$id)
compare$packages_diff

print("sensor values differences")
compare$sensor_1d_diff = dataset_processed$send_unified$sensor_1d - 
  dataset_processed$receive_unified$sensor_1d
compare$sensor_1d_diff 
```

## Values
```{r}
#linecolors <- c("#714C02", "#01587A", "#024E37")
linecolors <- c("#714C02", "#01587A")
fillcolors <- c("#9D6C06", "#077DAA")


p <- ggplot(dataset_processed$send_rec, aes(time, sensor_1d, 
    colour = set_name, fill = set_name, shape = set_name, size = set_name)) +
  geom_point(alpha = 0.5, size = 3) +
  scale_color_manual(values=linecolors) +
  scale_size_manual(values = c(5,10)) + # fixme
  scale_fill_manual(values=fillcolors) +
  scale_shape_manual(values= c(21, 25))
p
```
```{r}
#p + geom_point(position=position_jitter(h=0.1, w=0.1), shape = 21, alpha = 0.5, size = 3) +
p + geom_point(aes(shape = factor(set_name), colour = sensor_1d, fill = sensor_1d),
  alpha = 0.5, size = 3)
  scale_color_manual(values=linecolors) +
  scale_fill_manual(values=fillcolors)
```


```{r}
# partially transparent points by setting `alpha = 0.5`
ggplot(mpg, aes(displ, cty, colour = drv, fill = drv)) +
  geom_point(position=position_jitter(h=0.1, w=0.1),
             shape = 21, alpha = 0.5, size = 3) +
  scale_color_manual(values=linecolors) +
  scale_fill_manual(values=fillcolors) +
  theme_bw()
```

```{r}
#plot(x = dataset_processed$receive$time, y = dataset_processed$receive$sensor_1d)
p <- ggplot(dataset_processed$receive, aes(time, sensor_1d))
p + geom_point(aes(colour = factor(id)))
p <- ggplot(dataset_processed$send, aes(time, sensor_1d))
p + geom_point()
```

# RF Quality
```{r}
rf_qlty <- list()
```


## TODO Data Throughput
todo : stress test, send intervals short

## Signal Strength
```{r}
p <- ggplot(dataset_processed$receive, aes(time, rssi))
p + geom_point(aes()) + ggtitle("Signastärke (RSSI Wert)")
#p + geom_point(aes(colour = factor(id)))
```

## Packet Reception Ratio

$$
\text { Packet Delivery Ratio } = \frac{\sum \text { Number of packet receive }}{\sum \text { Number of packet send }}
$$
```{r}
print("packet reception ratio")
rf_qlty$package_reception_ratio = length(dataset_processed$receive_unified) /
  length(dataset_processed$send_unified)
rf_qlty$package_reception_ratio
```


## Compare General
**Overall**
```{r}
compare$send_rec_summary
```

```{r}
compare$send_rec_summary$diffs.table
print(compare$send_rec_summary$frame.summary.table)
```



```{r}
compare$send_rec$vars.summary
```


## more
- mulitple senders
  - data collision
- throughput
  - coding rate
  
### optimiatzation
- data rate
- data collision, send algorithm

