---
title: "Radio analysis"
output: html_document
date: "2023-12-21"
---

```{r}
#install.packages("RSQLite")
#install.packages("anytime")
#install.packages("sf")
#install.packages('osmdata')
```

# Pre-settings

**Libraries**

```{r}
library(DBI)
library(anytime)
library(dplyr)

library(sf)
library(ggplot2)
library(ggmap)
library(osmdata)
```

**Environment**

```{r}
rm(list=ls())
setwd(getwd())
```

# Measurment
```{r}
gateway <- list()
gateway$locaiton = "Druckerraum"
```


# Data source

```{r}
db_info <- list(
  filename = "20231216_p2p_hslu.db"
)
db_info$path = file.path("raw", db_info$filename)

db_con <- dbConnect(RSQLite::SQLite(), db_info$path)

db_tables <- list(
  sensor_data = "sensornodes_sensor_data"
)

# merge
db <- list(con = db_con, info = db_info, tables = db_tables)
rm(db_con, db_info, db_tables)
```

## Extract raw data

```{r}
dbListTables(db$con)
dbListFields(db$con, db$tables$sensor_data)
```

```{r}
sensornode_10_raw <- list()
# temperature 1
res <- dbSendQuery(db$con, "SELECT * FROM sensornodes_sensor_data WHERE sensor_id = 1 AND sensornode_id")
sensornode_10_raw$temperature_1  <- dbFetch(res)
dbClearResult(res)
# temperature 1
res <- dbSendQuery(db$con, "SELECT * FROM sensornodes_sensor_data WHERE sensor_id = 2 AND sensornode_id")
sensornode_10_raw$temperature_2  <- dbFetch(res)
dbClearResult(res)
```

```{r}
dbDisconnect(db$con)
```

# Modify
```{r}
node_10_temperature_1 <- sensornode_10_raw$temperature_1
node_10_temperature_1$sensor_type <- "Temperature 1"

node_10_temperature_2 <- sensornode_10_raw$temperature_2
node_10_temperature_2$sensor_type <- "Temperature 2"
```

**Time addition**
```{r}
node_10_temperature_1$time_unix_s <- 
  sensornode_10_raw$temperature_1$time_receive_unix_s + 
  sensornode_10_raw$temperature_1$time_rtc_s

node_10_temperature_2$time_unix_s <- 
  sensornode_10_raw$temperature_2$time_receive_unix_s + 
  sensornode_10_raw$temperature_2$time_rtc_s
```

**Time conversion**
```{r include=FALSe} 
node_10_temperature_1$time_cet <-
  as.POSIXct(node_10_temperature_1$time_receive_unix_s, format = "%Y-%m-%d %H:%M:%S", tz = "CET")

node_10_temperature_2$time_cet<-
  as.POSIXct(node_10_temperature_2$time_receive_unix_s, format = "%Y-%m-%d %H:%M:%S", tz = "CET")
```


**Location Coordinates**
```{r}
locations <- data.frame(
  location_name = character(),
  gps_latitude = numeric(),
  gps_longitude = numeric(),
  map_latitude = numeric(),
  map_longitude = numeric()
)

loc_1 <- data.frame(
  location_name = "E542",
  gps_latitude = '47°00.8575',
  gps_longitude = '008°18.3218',
  map_latitude = 2665888.34,
  map_longitude = 1207377.10
)
loc_2 <- data.frame(
  location_name = "D302",
  gps_latitude = '47°00.8709',
  gps_longitude = '008°18.3424',
  map_latitude = 0,
  map_longitude = 0
)
loc_3 <- data.frame(
  location_name = "F3xx",
  gps_latitude = '47°00.8095',
  gps_longitude = '008°18.3389',
  map_latitude = 0,
  map_longitude = 0
)
loc_4 <- data.frame(
  location_name = "B332",
  gps_latitude = '47°00.8620',
  gps_longitude = '008°18.3812',
  map_latitude = 0,
  map_longitude = 0
)
loc_5 <- data.frame(
  location_name = "B200",
  gps_latitude = '47°00.8404',
  gps_longitude = '008°18.3415',
  map_latitude = 0,
  map_longitude = 0
)
loc_6 <- data.frame(
  location_name = "A4",
  gps_latitude = 'none',
  gps_longitude = 'none',
  map_latitude = 0,
  map_longitude = 0
)

locations <- rbind(locations, loc_1, loc_2, loc_3, loc_4)
rm(loc_1, loc_2, loc_3, loc_4, loc_5, loc_6)
print(locations)
```


## Location time mapping
### temperature 1
Map location to time
```{r}
node_10_temperature_1$location <- ""
node_10_temperature_1 <- node_10_temperature_1 %>% 
   mutate(location = ifelse(
    between(
      time_cet, 
      as.POSIXct("2023-12-16 14:35:00", tz = "CET"),
      as.POSIXct("2023-12-16 14:40:00", tz = "CET")
    ),
    "Trakt 4 E542 1.OG",
    ifelse(
      between(
        time_cet, 
        as.POSIXct("2023-12-16 15:00:00", tz = "CET"),
        as.POSIXct("2023-12-16 15:15:30", tz = "CET")
      ),
      "Trakt 3 D302 EG",
    ifelse(
      between(
        time_cet, 
        as.POSIXct("2023-12-16 15:17:00", tz = "CET"),
        as.POSIXct("2023-12-16 15:41:00", tz = "CET")
      ),
      "Trakt 3 F3xx",
    ifelse(
      between(
        time_cet, 
        as.POSIXct("2023-12-16 15:48:00", tz = "CET"),
        as.POSIXct("2023-12-16 15:55:00", tz = "CET")
      ),
      "Trakt 3 B332",
    ifelse(
      between(
        time_cet, 
        as.POSIXct("2023-12-16 15:57:00", tz = "CET"),
        as.POSIXct("2023-12-16 16:18:00", tz = "CET")
      ),
      "Trakt 2 B200",
    ifelse(
      between(
        time_cet, 
        as.POSIXct("2023-12-16 16:19:00", tz = "CET"),
        as.POSIXct("2023-12-16 16:45:00", tz = "CET")
      ),
      "Trakt 1 A4",
      "undefined"
    ))))))) #ifelse close
```
### temperature 2
```{r}
node_10_temperature_2$location <- ""
node_10_temperature_2 <- node_10_temperature_2 %>%
   mutate(location = ifelse(
    between(
      time_cet, 
      as.POSIXct("2023-12-16 14:35:00", tz = "CET"),
      as.POSIXct("2023-12-16 14:40:00", tz = "CET")
    ),
    "Trakt 4 E542 1.OG",
    ifelse(
      between(
        time_cet, 
        as.POSIXct("2023-12-16 15:00:00", tz = "CET"),
        as.POSIXct("2023-12-16 15:15:30", tz = "CET")
      ),
      "Trakt 3 D302 EG",
    ifelse(
      between(
        time_cet, 
        as.POSIXct("2023-12-16 15:17:00", tz = "CET"),
        as.POSIXct("2023-12-16 15:41:00", tz = "CET")
      ),
      "Trakt 3 F3xx",
    ifelse(
      between(
        time_cet, 
        as.POSIXct("2023-12-16 15:48:00", tz = "CET"),
        as.POSIXct("2023-12-16 15:55:00", tz = "CET")
      ),
      "Trakt 3 B332",
    ifelse(
      between(
        time_cet, 
        as.POSIXct("2023-12-16 15:57:00", tz = "CET"),
        as.POSIXct("2023-12-16 16:18:00", tz = "CET")
      ),
      "Trakt 2 B200",
    ifelse(
      between(
        time_cet, 
        as.POSIXct("2023-12-16 16:19:00", tz = "CET"),
        as.POSIXct("2023-12-16 16:45:00", tz = "CET")
      ),
      "Trakt 1 A4",
      "undefined"
    ))))))) #ifelse close
```

# Analysis
**Adjust time range of measuremnts**
```{r}
# Combine both datasets
combined_data_tmp <- rbind(node_10_temperature_1, node_10_temperature_2)

## filter: outlayers
combined_data <- combined_data_tmp[
  combined_data_tmp$time_cet <= as.POSIXct("2023-12-16 16:19:00", tz = "CET"),
]
```
**Measurment separators**
```{r}
locations_time_separation <- c (
  as.POSIXct("2023-12-16 14:35:00", tz = "CET"), 
  as.POSIXct("2023-12-16 15:00:00", tz = "CET"),
  as.POSIXct("2023-12-16 15:27:00", tz = "CET"),
  as.POSIXct("2023-12-16 15:48:00", tz = "CET"),
  as.POSIXct("2023-12-16 15:57:00", tz = "CET")
#  as.POSIXct("2023-12-16 16:19:00", tz = "CET")
)
```
## Temperature
```{r}
library(lubridate)
# Create a plot for both datasets
x_offset = 0.1
y_offset_min = 2
tmp_middle = median(combined_data$sensor_value) + 0.1


results_plots_nodes_values <- ggplot(combined_data, aes(x = time_cet, y = sensor_value, color = sensor_type)) +
  geom_point() +
  geom_vline(xintercept = locations_time_separation, 
    linetype="dotted") +
  annotate("text", x = locations_time_separation[1] - minutes(2), y = tmp_middle, label = "E542", angle = 90) +
  annotate("text", x = locations_time_separation[2] - minutes(2), y = tmp_middle, label = "D302", angle = 90) +
  annotate("text", x = locations_time_separation[3] - minutes(2), y = tmp_middle, label = "F3xx", angle = 90) +
  annotate("text", x = locations_time_separation[4] - minutes(2), y = tmp_middle, label = "B332", angle = 90) +
  annotate("text", x = locations_time_separation[5] - minutes(2), y = tmp_middle, label = "A4", angle = 90) +
  labs(x = "Uhrzeit", y = "Temperature [°C]"
    #, title = "Zeit vs Temperatur"
    ) +
  labs(color = "Sensornr.") +
  theme(legend.position = "bottom")
results_plots_nodes_values
```

## Split data per location
```{r}
locations_data <- list()
locations_data$e542 <- filter(node_10_temperature_1, location == "Trakt 4 E542 1.OG")
locations_data$b200 <- filter(node_10_temperature_1, location == "Trakt 2 B200")
locations_data$f3xx <- filter(node_10_temperature_1, location == "Trakt 3 F3xx")
locations_data$a4 <- filter(node_10_temperature_1, location == "Trakt 1 A4")
locations_data$undefined <- filter(node_10_temperature_1, location == "undefined")

summary(locations_data)
```

## Packet Reception Ratio

$$
\text { Packet Delivery Ratio } = \frac{\sum \text { Number of packet receive }}{\sum \text { Number of packet send }}
$$

```{r}
locations_results <- list()
locations_results$e542 <- ""
locations_results$b200 <- ""
locations_results$f3xx<- ""
locations_results$a4 <- ""
locations_results$undefined <- ""
```

```{r}
number_received = length(locations_data$e542$measure_nr)
number_total = max(locations_data$e542$measure_nr) - min (locations_data$e542$measure_nr) + 1
locations_results$e542$pdf = number_received / number_total
locations_results$e542$pdf
#
number_received = length(locations_data$b200$measure_nr)
number_total = max(locations_data$b200$measure_nr) - min (locations_data$b200$measure_nr) + 1
locations_results$b200$pdf = number_received / number_total
locations_results$b200$pdf
#
number_received = length(locations_data$f3xx$measure_nr)
number_total = max(locations_data$f3xx$measure_nr) - min (locations_data$f3xx$measure_nr) + 1
locations_results$f3xx$pdf = number_received / number_total
locations_results$f3xx$pdf
#
number_received = length(locations_data$a4$measure_nr)
number_total = max(locations_data$a4$measure_nr) - min (locations_data$a4$measure_nr) + 1
locations_results$a4$pdf = number_received / number_total
locations_results$a4$pdf
#
number_received = length(locations_data$undef$measure_nr)
number_total = max(locations_data$undef$measure_nr) - min (locations_data$undef$measure_nr) + 1
locations_results$undef$pdf = number_received / number_total
locations_results$undef$pdf
```
**Problem**
Fehler bei measure_nr, kann nicht verwendet werden.

## Differences with plots
```{r}
globvar <- list()
globvar$temperature_time_sample_s = 5
globvar$temperature_time_sample_upper_s = 6
globvar$temperature_time_sample_threshold_s = 10
```


**E542**
```{r}
time_sample_s = globvar$temperature_time_sample_s
#time_sample_upper_s = globvar$temperature_time_sample_upper_s
time_sample_threshold_s = globvar$temperature_time_sample_threshold_s

i <- 2
i_max <- length(locations_data$e542$id)
locations_data$e542$time_diffs <- c()
while (i <= i_max) {
  locations_data$e542$time_diffs[i-1] = 
    locations_data$e542$time_rtc_s[i] - 
    locations_data$e542$time_rtc_s[i-1]
  #print(i)
  i <- i + 1
}
locations_data$e542$time_diffs

df <- data.frame(Index = 1:length(locations_data$e542$time_diffs), Value = locations_data$e542$time_diffs)

# plot: Line plot
results_e542_plot_line <- ggplot(df, aes(x = Index, y = Value)) +
  geom_point() +
  geom_line(linetype = "dotted", color = "darkgrey") +
  geom_hline(yintercept = time_sample_s, linetype="dotted", color="red") +
#  geom_hline(yintercept = time_sample_upper_s, linetype="dotted", color="red") +
  geom_hline(yintercept = time_sample_threshold_s, linetype="dashed", color="red") +
#  ggtitle("Line Plot of Data") +
  xlab("Index") +
ylab("Zeitdifferenz [s]")

# plot: Boxplot
df <- data.frame(Value = locations_data$e542$time_diffs)

results_e542_plot_box <- ggplot(df, aes(y = Value)) +
  geom_boxplot() +
 #  ggtitle("Boxplot of Data") +
  ylab("Zeitdifferenz [s]") +
  xlab("") # fix: same plot heigths

results_e542_plot_line
results_e542_plot_box
```
**B200**
```{r}
time_sample_s = globvar$temperature_time_sample_s
#time_sample_upper_s = globvar$temperature_time_sample_upper_s
time_sample_threshold_s = globvar$temperature_time_sample_threshold_s

i <- 2
i_max <- length(locations_data$b200$id)
locations_data$b200$time_diffs <- c()
while (i <= i_max) {
  locations_data$b200$time_diffs[i-1] = 
    locations_data$b200$time_rtc_s[i] - 
    locations_data$b200$time_rtc_s[i-1]
  #print(i)
  i <- i + 1
}
locations_data$b200$time_diffs

df <- data.frame(Index = 1:length(locations_data$b200$time_diffs),
  Value = locations_data$b200$time_diffs)

# plot: Line plot
results_b200_plot_line <- ggplot(df, aes(x = Index, y = Value)) +
  geom_point(size = 0.75) +
  geom_line(linetype = "dotted", color = "darkgrey") + 
  geom_hline(yintercept = time_sample_s, linetype="dotted", color="red") +
#  geom_hline(yintercept = time_sample_upper_s, linetype="dotted", color="red") +
  geom_hline(yintercept = time_sample_threshold_s, linetype="dashed", color="red") +
#  ggtitle("Line Plot of Data") +
  xlab("Index") +
  ylab("Zeitdifferenz [s]")

# plot: Boxplot
df <- data.frame(Value = locations_data$b200$time_diffs)

results_b200_plot_box <- ggplot(df, aes(y = Value)) +
  geom_boxplot() +
 #  ggtitle("Boxplot of Data") +
  ylab("Zeitdifferenz [s]")

results_b200_plot_line
results_b200_plot_box
```
**F3xx**
```{r}
time_sample_s = globvar$temperature_time_sample_s
#time_sample_upper_s = globvar$temperature_time_sample_upper_s
time_sample_threshold_s = globvar$temperature_time_sample_threshold_s

i <- 2
i_max <- length(locations_data$f3xx$id)
locations_data$f3xx$time_diffs <- c()
while (i <= i_max) {
  locations_data$f3xx$time_diffs[i-1] = 
    locations_data$f3xx$time_rtc_s[i] - 
    locations_data$f3xx$time_rtc_s[i-1]
  #print(i)
  i <- i + 1
}
locations_data$f3xx$time_diffs

df <- data.frame(Index = 1:length(locations_data$f3xx$time_diffs), Value = locations_data$f3xx$time_diffs)

# plot: Line plot
results_f3xx_plot_line <- ggplot(df, aes(x = Index, y = Value)) +
#  geom_point() +
  geom_line(linetype = "solid", color = "black") + 
  geom_hline(yintercept = time_sample_s, linetype="dotted", color="red") +
#  geom_hline(yintercept = time_sample_upper_s, linetype="dotted", color="red") +
  geom_hline(yintercept = time_sample_threshold_s, linetype="dashed", color="red") +
#  ggtitle("Line Plot of Data") +
  xlab("Index") +
  ylab("Zeitdifferenz [s]")

# plot: Boxplot
df <- data.frame(Value = locations_data$f3xx$time_diffs)

results_f3xx_plot_box <- ggplot(df, aes(y = Value)) +
  geom_boxplot() +
 #  ggtitle("Boxplot of Data") +
  ylab("Zeitdifferenz [s]")

## filter: outlayers
locations_results$f3xx$time_diffs_filter <- 
  locations_data$f3xx$time_diffs[
    locations_data$f3xx$time_diffs <= time_sample_threshold_s
]

diffs_filter = locations_results$f3xx$time_diffs_filter

df <- data.frame(Index = 1:length(diffs_filter), Value = diffs_filter)

# plot: Line plot
results_f3xx_plot_line_filtered <- ggplot(df, aes(x = Index, y = Value)) +
  geom_point() +
  geom_line(linetype = "dotted", color = "darkgrey") + 
  geom_hline(yintercept = time_sample_s, linetype="dotted", color="red") +
#  geom_hline(yintercept = time_sample_upper_s, linetype="dotted", color="red") +
  geom_hline(yintercept = time_sample_threshold_s, linetype="dashed", color="red") +
#  ggtitle("Line Plot of Data") +
  xlab("Index") +
  ylab("Zeitdifferenz [s]")

# plot: Boxplot
df <- data.frame(Value = diffs_filter)

results_f3xx_plot_box_filtered <- ggplot(df, aes(y = Value)) +
  geom_boxplot() +
 #  ggtitle("Boxplot of Data") +
  ylab("Zeitdifferenz [s]")

results_f3xx_plot_line
results_f3xx_plot_box
results_f3xx_plot_line_filtered
results_f3xx_plot_box_filtered
```
**A4**
```{r}
time_sample_s = globvar$temperature_time_sample_s
#time_sample_upper_s = globvar$temperature_time_sample_upper_s
time_sample_threshold_s = globvar$temperature_time_sample_threshold_s

i <- 2
i_max <- length(locations_data$a4$id)
locations_data$a4$time_diffs <- c()
while (i <= i_max) {
  locations_data$a4$time_diffs[i-1] = 
    locations_data$a4$time_rtc_s[i] - 
    locations_data$a4$time_rtc_s[i-1]
  #print(i)
  i <- i + 1
}
locations_data$a4$time_diffs

# filter high values
locations_results$a4$time_diffs_filter <- locations_data$a4$time_diffs[
  locations_data$a4$time_diffs >= -1000 &
  locations_data$a4$time_diffs <= 1000
]

diffs_filter = locations_results$a4$time_diffs_filter

df <- data.frame(Index = 1:length(diffs_filter), Value = diffs_filter)

# plot: Line plot
results_a4_plot_line <- ggplot(df, aes(x = Index, y = Value)) +
#  geom_point() +
  geom_line(linetype = "solid", color = "black") + 
  geom_hline(yintercept = time_sample_s, linetype="dotted", color="red") +
#  geom_hline(yintercept = time_sample_upper_s, linetype="dotted", color="red") +
  geom_hline(yintercept = time_sample_threshold_s, linetype="dashed", color="red") +
#  ggtitle("Line Plot of Data") +
  xlab("Index") +
  ylab("Zeitdifferenz [s]")

# plot: Boxplot
df <- data.frame(Value = diffs_filter)

results_a4_plot_box <- ggplot(df, aes(y = Value)) +
  geom_boxplot() +
 #  ggtitle("Boxplot of Data") +
  ylab("Zeitdifferenz [s]")

## filter: outlayers
locations_results$a4$time_diffs_filter2 <- 
  locations_data$a4$time_diffs[
      locations_data$a4$time_diffs >= -1000 &
    locations_data$a4$time_diffs <= 1000 &
    locations_data$a4$time_diffs <= time_sample_threshold_s
]
diffs_filter2 = locations_results$a4$time_diffs_filter2

df <- data.frame(Index = 1:length(diffs_filter2), Value = diffs_filter2)

# plot: Line plot
results_a4_plot_line_filtered <- ggplot(df, aes(x = Index, y = Value)) +
  geom_point() +
  geom_line(linetype = "dotted", color = "darkgrey") + 
  geom_hline(yintercept = time_sample_s, linetype="dotted", color="red") +
#  geom_hline(yintercept = time_sample_upper_s, linetype="dotted", color="red") +
  geom_hline(yintercept = time_sample_threshold_s, linetype="dashed", color="red") +
#  ggtitle("Line Plot of Data") +
  xlab("Index") +
  ylab("Zeitdifferenz [s]")

# plot: Boxplot
df <- data.frame(Value = diffs_filter2)

results_a4_plot_box_filtered <- ggplot(df, aes(y = Value)) +
  geom_boxplot() +
# #  ggtitle("Boxplot of Data") +
  ylab("Zeitdifferenz [s]")

results_a4_plot_line
results_a4_plot_box
results_a4_plot_line_filtered
results_a4_plot_box_filtered
```

## Geolocation
- Quelle Karte : https://www.geo.lu.ch/meta?metauid=UP10FARB_DS
  - Übersichtsplan 1:10'000 (UP10), farbig
- https://www.rdocumentation.org/packages/terra/versions/1.5-21/topics/crop


```{r}
library(terra)

tif_file <- terra::rast("UP10FARB_V1_RAS_T11504.tif")
e <- terra::ext(-5, 5, -5, 5)
e <- ext(2665820, 2666050, 1207200, 1207500)
tif_crop <- terra::crop(tif_file, e)
#plot(tif_crop)
```

**Convert degree-minute DD°MM.mmmm to decimal degrees DD.dddd**
```{r}
lat_degrees <- as.numeric(substring(locations$gps_latitude, 1, 2)) # vor °
lat_minutes <- as.numeric(substring(locations$gps_latitude, 4)) # nach °
locations$gps_latitude_decdeg<- lat_degrees + lat_minutes / 60
#print(locations$gps_latitude_decdeg)

lon_degrees <- as.numeric(substring(locations$gps_longitude, 1, 3)) # vor °
lon_minutes <- as.numeric(substring(locations$gps_longitude, 5)) # nach °
locations$gps_longitude_decdeg <- lon_degrees + lon_minutes / 60
#print(locations$gps_longitude_decdeg)

# coordinates wgs84 geometries
epsg_wgs84 = 4326
sf_coordinates_gps <- st_as_sf(locations, coords = c("gps_longitude_decdeg", "gps_latitude_decdeg"), crs = epsg_wgs84) 
print(sf_coordinates_gps)

# convert wgs84 to swiss format
#epsg_lv03 = 4326
epsg_lv95 = 2056
locations$gps_epsg205_lv95 <- st_transform(sf_coordinates_gps, crs = epsg_lv95)
print(locations$gps_epsg205_lv95)
```
```{r}
sf_coordinates_map <- st_as_sf(locations, coords = c("map_longitude", "map_latitude"), crs = epsg_lv95)
#print(sf_coordinates_map)

locations$map_epsg205_lv95 <- st_transform(sf_coordinates_map, crs = epsg_lv95)
print(locations$map_epsg205_lv95)
```

**Plot GPS Location**
```{r}
gps_points <- vect(locations$gps_epsg205_lv95$geometry)
map_points <- vect(locations$map_epsg205_lv95$geometry)
#map_points <- c(locations$map_latitude, locations$map_longitude)
#locations2_swiss <- vect(matrix(c(2665902, 1207390), ncol = 2), crs = epsg_lv95)
# Plot the point using terra

terra::plot(tif_crop)
terra::points(gps_points, col = "red", pch = 16, cex = 1.5)
# todo : fixme
#terra::points(map_points, col = "blue", pch = 16, cex = 1.5)
```



# Post Actions
## Save Plots
```{r}
ggsave("export/nodes_temperatures.png", plot = results_plots_nodes_values, width = 10, height = 5, dpi = 600)
#
ggsave("export/results_e542_plot_line.png", plot = results_e542_plot_line, width = 6.2, height = 5, dpi = 600)
ggsave("export/results_e542_plot_box.png", plot = results_e542_plot_box, width = 3.8, height = 5, dpi = 600)
#
ggsave("export/results_b200_plot_line.png", plot = results_b200_plot_line, width = 6.2, height = 5, dpi = 600)
ggsave("export/results_b200_plot_box.png", plot = results_b200_plot_box, width = 3.8, height = 5, dpi = 600)
#
ggsave("export/results_f3xx_plot_line.png", plot = results_f3xx_plot_line, width = 6.2, height = 5, dpi = 600)
ggsave("export/results_f3xx_plot_box.png", plot = results_f3xx_plot_box, width = 3.8, height = 5, dpi = 600)
ggsave("export/results_f3xx_plot_line_filtered.png", plot = results_f3xx_plot_line_filtered, width = 6.2, height = 5, dpi = 600)
ggsave("export/results_f3xx_plot_box_filtered.png", plot = results_f3xx_plot_box_filtered, width = 3.8, height = 5, dpi = 600)
#
ggsave("export/results_a4_plot_line.png", plot = results_a4_plot_line, width = 6.2, height = 5, dpi = 600)
ggsave("export/results_a4_plot_box.png", plot = results_a4_plot_box, width = 3.8, height = 5, dpi = 600)
ggsave("export/results_a4_plot_line_filtered.png", plot = results_a4_plot_line_filtered, width = 6.2, height = 5, dpi = 600)
ggsave("export/results_a4_plot_box_filtered.png", plot = results_a4_plot_box_filtered, width = 3.8, height = 5, dpi = 600)
```




