---
title: "Radio analysis"
output: html_document
date: "2023-12-21"
---

```{r}
#install.packages("RSQLite")
#install.packages("anytime")
#install.packages("sf")
#install.packages('osmdata')
```

# Pre-settings

**Libraries**

```{r}
library(DBI)
library(anytime)
library(dplyr)

library(sf)
library(ggplot2)
library(ggmap)
library(osmdata)
```

**Environment**

```{r}
rm(list=ls())
setwd(getwd())
```

# Measurment
```{r}
gateway <- list()
gateway$locaiton = "Druckerraum"
```


# Data source

```{r}
db_info <- list(
  filename = "20231216_p2p_hslu.db"
)
db_info$path = file.path("raw", db_info$filename)

db_con <- dbConnect(RSQLite::SQLite(), db_info$path)

db_tables <- list(
  sensor_data = "sensornodes_sensor_data"
)

# merge
db <- list(con = db_con, info = db_info, tables = db_tables)
rm(db_con, db_info, db_tables)
```

## Extract raw data

```{r}
dbListTables(db$con)
dbListFields(db$con, db$tables$sensor_data)
```

```{r}
received_data_raw <- list()

received_sensornode_10_raw <- list()
# temperature 1
res <- dbSendQuery(db$con, "SELECT * FROM sensornodes_sensor_data WHERE sensor_id = 1 AND sensornode_id")
received_sensornode_10_raw$temperature_1  <- dbFetch(res)
dbClearResult(res)
# temperature 1
res <- dbSendQuery(db$con, "SELECT * FROM sensornodes_sensor_data WHERE sensor_id = 2 AND sensornode_id")
received_sensornode_10_raw$temperature_2  <- dbFetch(res)
dbClearResult(res)
```

```{r}
dbDisconnect(db$con)
```

# Modify
```{r}
df_temperature_1 <- received_sensornode_10_raw$temperature_1
```


**Time conversion**
```{r include=FALSe} 
df_temperature_1$time_receive_cet <-
  as.POSIXct(df_temperature_1$time_receive_unix_s, format = "%Y-%m-%d %H:%M:%S", tz = "CET")
```

**Location Coordinates**
```{r}
locations <- data.frame(
  location_name = character(),
  latitude = numeric(),
  longitude = numeric()
)

loc_1 <- data.frame(
  location_name = "E542",
  latitude = '47°00.8575',
  longitude = '008°18.3218'
)
loc_2 <- data.frame(
  location_name = "D302",
  latitude = '47°00.8709',
  longitude = '008°18.3424'
)
loc_3 <- data.frame(
  location_name = "F3xx",
  latitude = '47°00.8095',
  longitude = '008°18.3389'
)
loc_4 <- data.frame(
  location_name = "B332",
  latitude = '47°00.8620',
  longitude = '008°18.3812'
)
loc_5 <- data.frame(
  location_name = "B200",
  latitude = '47°00.8404',
  longitude = '008°18.3415'
)
loc_6 <- data.frame(
  location_name = "A4",
  latitude = 'none',
  longitude = 'none'
)

locations <- rbind(locations, loc_1, loc_2, loc_3, loc_4)
rm(loc_1, loc_2, loc_3, loc_4, loc_5, loc_6)
print(locations)
```


**Location time mapping**
Map location to time
```{r}
df_temperature_1$location <- ""

df_temperature_1 <- df_temperature_1 %>% 
   mutate(location = ifelse(
    between(
      time_receive_cet, 
      as.POSIXct("2023-12-16 14:35:00", tz = "CET"),
      as.POSIXct("2023-12-16 14:40:00", tz = "CET")
    ),
    "Trakt 4 E542 1.OG",
    ifelse(
      between(
        time_receive_cet, 
        as.POSIXct("2023-12-16 15:00:00", tz = "CET"),
        as.POSIXct("2023-12-16 15:15:30", tz = "CET")
      ),
      "Trakt 3 D302 EG",
    ifelse(
      between(
        time_receive_cet, 
        as.POSIXct("2023-12-16 15:17:00", tz = "CET"),
        as.POSIXct("2023-12-16 15:41:00", tz = "CET")
      ),
      "Trakt 3 F3xx",
    ifelse(
      between(
        time_receive_cet, 
        as.POSIXct("2023-12-16 15:48:00", tz = "CET"),
        as.POSIXct("2023-12-16 15:55:00", tz = "CET")
      ),
      "Trakt 3 B332",
    ifelse(
      between(
        time_receive_cet, 
        as.POSIXct("2023-12-16 15:57:00", tz = "CET"),
        as.POSIXct("2023-12-16 16:18:00", tz = "CET")
      ),
      "Trakt 2 B200",
    ifelse(
      between(
        time_receive_cet, 
        as.POSIXct("2023-12-16 16:19:00", tz = "CET"),
        as.POSIXct("2023-12-16 16:45:00", tz = "CET")
      ),
      "Trakt 1 A4",
      "undefined"
    ))))))) #ifelse close
```
```{r}
```




**Create processed**
```{r}
received_sensornode_10_processed <- list()
received_sensornode_10_processed$temperature_1 = df_temperature_1
```

# Analysis

```{r}


```

# Results
## Temperature
```{r}
ggplot(received_sensornode_10_raw$temperature_1, aes(x = received_sensornode_10_raw$temperature_1$time_receive_cet,
  y = received_sensornode_10_raw$temperature_1$sensor_value)) +
  geom_line() +
  geom_point() +
  labs(x = "Time", y = "Values", title = "Time vs Values")
```
## Packet Reception Ratio

$$
\text { Packet Delivery Ratio } = \frac{\sum \text { Number of packet receive }}{\sum \text { Number of packet send }}
$$
### Data per location
```{r}
data_locations <- list()
data_locations$e542 <- filter(df_temperature_1, location == "Trakt 4 E542 1.OG")
data_locations$b200 <- filter(df_temperature_1, location == "Trakt 2 B200")
data_locations$f3xx <- filter(df_temperature_1, location == "Trakt 3 F3xx")
data_locations$a4 <- filter(df_temperature_1, location == "Trakt 1 A4")
data_locations$undefined <- filter(df_temperature_1, location == "undefined")

summary(data_locations)
```


## Geolocation
- Quelle Karte : https://www.geo.lu.ch/meta?metauid=UP10FARB_DS
  - Übersichtsplan 1:10'000 (UP10), farbig
- https://www.rdocumentation.org/packages/terra/versions/1.5-21/topics/crop


```{r}
library(terra)

tif_file <- terra::rast("UP10FARB_V1_RAS_T11504.tif")
e <- terra::ext(-5, 5, -5, 5)
e <- ext(2665820, 2666050, 1207200, 1207500)
tif_crop <- terra::crop(tif_file, e)
#plot(tif_crop)
```

**Convert degree-minute DD°MM.mmmm to decimal degrees DD.dddd**
```{r}
lat_degrees <- as.numeric(substring(locations$latitude, 1, 2)) # vor °
lat_minutes <- as.numeric(substring(locations$latitude, 4)) # nach °
locations$latitude_decdeg<- lat_degrees + lat_minutes / 60
#print(locations$latitude_decdeg)

lon_degrees <- as.numeric(substring(locations$longitude, 1, 3)) # vor °
lon_minutes <- as.numeric(substring(locations$longitude, 5)) # nach °
locations$longitude_decdeg <- lon_degrees + lon_minutes / 60
#print(locations$longitude_decdeg)

epsg_wgs84 = 4326
sf_coordinates <- st_as_sf(locations, coords = c("longitude_decdeg", "latitude_decdeg"), crs = epsg_wgs84) # 
print(sf_coordinates)

#epsg_lv03 = 4326
epsg_lv95 = 2056
locations$epsg205_lv95<- st_transform(sf_coordinates, crs = epsg_lv95)
print(locations_swiss$geometry)
```

**Plot GPS Location**
```{r}
points <- vect(locations$epsg205_lv95$geometry)
#locations2_swiss <- vect(matrix(c(2665902, 1207390), ncol = 2), crs = epsg_lv95)
# Plot the point using terra

terra::plot(tif_crop)
terra::points(points, col = "red", pch = 16, cex = 1.5)
```







